---
title: "Music Insight Regression"
author: "Kevin Chen"
output:
  html_document: default
  word_document: default
  pdf_document: default
  df_print: paged
---



```{r}
include <- function(library_name){
  if( !(library_name %in% installed.packages()) )
    install.packages(library_name) 
  library(library_name, character.only=TRUE)
}

include("dplyr")
include("caret")
include("tidyverse")
include("knitr")
include("ggplot2")
purl("MusicInsights.Rmd", output = "part1.r")
source("part1.r")
```
import all of the music insight files

```{r}
Person$average_rating <-sapply(Person$pseudonym,
      function(name){ 
        hold1 <- Charts$Rating[Charts$pseudonym == name] 
        average <-mean(hold1)
        return(average)
      }
    )

#view(average_rating)
```
This take the average of all the rating for each Person pseudonym

```{r}
Person<-na.omit(Person)
#Person$time_submitted <- NULL
```
This remove all NA because the createDataPartition dont work with missing value or NA.
The commit out section was trying to remove time_submitted for train_model to fix certain issue but didnt work.

```{r}
set.seed(385)
sample_selection <- createDataPartition(Person$average_rating, p = 0.75, list = FALSE)
train <- Person[sample_selection]
test <- Person[-sample_selection]

train_model <- lm(Person, formual = average_rating ~ sex + acacdemic_level + Major)

```
In this R code the createDataPartition work as intented but wasnt able to get the random sample set due to an error "Error: Must use a vector in `[`, not an object of class matrix.". The same is said with the train_model as it was able to run but has extra argument the effect the final result.(The train_model only run if you commit out train and test R code)

```{r}
summary(train_model)
```
Trying to get a visual of train_model. If you run the code by skipping train and test part of R code by commenting it out you get as shown with time_submitted seeming to polluted the data. Overall not able to get much.


